Clustering exploration for `r params$library_id`

### 2024-11-20 analyses/cell-type-ewings/template_notebooks/clustering-workflow/01-clustering-metrics.Rmd
change back to current

---
title: "Clustering exploration for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: "SCPCL000822"
  sce_file: "../../../../data/2024-07-08/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  cluster_results_file: "SCPCL000822_clusters.tsv"
  nn_range: !r seq(5, 40, 5)
  louvain_res_range: !r c(0.5, 1, 1.5)
  mod_res_range: !r c(0.5, 1, 1.5)
  cpm_res_range: !r c(0.001, 0.005, 0.01)
---

>>>>

---
title: "Clustering exploration for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: "SCPCL000822"
  sce_file: "../../../../data/current/SCPCP000015/SCPCS000490/SCPCL000822_processed.rds"
  cluster_results_file: "SCPCL000822_clusters.tsv"
  nn_range: !r seq(5, 40, 5)
  louvain_res_range: !r c(0.5, 1, 1.5)
  mod_res_range: !r c(0.5, 1, 1.5)
  cpm_res_range: !r c(0.001, 0.005, 0.01)
---
